---
title: "Iteration and listcols"
author: "Tianyou Wang"
date: "2022-11-18"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(rvest)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Lists

In R, vectors are limited to a single data class – all elements have to be characters, or all numeric, or all logical. Trying to join the following vectors will result in coersion, as would creating vectors of mixed types.

```{r}
vec_numeric = 5:8
vec_logical = c(TRUE, TRUE, FALSE, TRUE, FALSE, FALSE)
mat =  matrix(1:8, nrow = 2, ncol = 4)
summary = summary(rnorm(100))
```

We can put anything in a list.This flexibility is great, but is offset by chunkiness. 

```{r}
l = list(
  vec_numeric = 5:8,
  vec_logical = c(TRUE, TRUE, FALSE, TRUE, FALSE, FALSE),
  mat =  matrix(1:8, nrow = 2, ncol = 4),
  summary = summary(rnorm(100))
)

l
```

Lists can be accessed using names or indices. The following commends give you the same thing.

```{r}
l$vec_numeric
l[[1]]
l[["vec_numeric"]]
```

Lists are really useful. Right now, we’ll use them to hold general inputs and outputs of iterative processes. Even more importantly, we’ll see that data frames are actually a very specific kind of list – one comprised of vectors of the same length – which is why they can store variables of different types.



## `for` loop

For this example, I’m going to start with the list defined below.

```{r}
list_norms = 
  list(
    a = rnorm(20, 3, 1),
    b = rnorm(20, 0, 5),
    c = rnorm(20, 10, .2),
    d = rnorm(20, -3, 1)
  )

is.list(list_norms)
```

```{r}
list_norms
```

I’d like to apply my simple `mean_and_sd` function from writing functions to each element of this list For completeness, that function is below.

```{r}
mean_and_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } 
  
  if (length(x) == 1) {
    stop("Cannot be computed for length 1 vectors")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)

  tibble(
    mean = mean_x, 
    sd = sd_x
  )
}
```

We can apply the `mean_and_sd` function to each element of list_norms using the lines below.

```{r}
mean_and_sd(list_norms[[1]])
mean_and_sd(list_norms[[2]])
mean_and_sd(list_norms[[3]])
mean_and_sd(list_norms[[4]])
```

Let's used a `for` loop.

Below, I define an output list with the same number of entries as my target dataframe; a sequence to iterate over; and a for loop body that applies the `mean_and_sd` function for each sequence element and saves the result. This will be much cleaner than using four almost-identical lines of code

```{r}
output = vector("list", length = 4)

for (i in 1:4) {
  output[[i]] = mean_and_sd(list_norms[[i]])
}
```

We already have our input list, `list_norms`. In the above code, we are creating the output list. Creating a vector that is a list, and the length equals to 4. The length just equal the length of input list. **`vector(mode = "logical/list etc", length = )`**


## maps


