---
title: "Iteration and listcols"
author: "Tianyou Wang"
date: "2022-11-18"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(rvest)
library(purrr)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Lists

In R, vectors are limited to a single data class – all elements have to be characters, or all numeric, or all logical. Trying to join the following vectors will result in coersion, as would creating vectors of mixed types.

```{r}
vec_numeric = 5:8
vec_logical = c(TRUE, TRUE, FALSE, TRUE, FALSE, FALSE)
mat =  matrix(1:8, nrow = 2, ncol = 4)
summary = summary(rnorm(100))
```

We can put anything in a list.This flexibility is great, but is offset by chunkiness. 

```{r}
l = list(
  vec_numeric = 5:8,
  vec_logical = c(TRUE, TRUE, FALSE, TRUE, FALSE, FALSE),
  mat =  matrix(1:8, nrow = 2, ncol = 4),
  summary = summary(rnorm(100))
)

l
```

Lists can be accessed using names or indices. The following commends give you the same thing.

```{r}
l$vec_numeric
l[[1]]
l[["vec_numeric"]]
```

Lists are really useful. Right now, we’ll use them to hold general inputs and outputs of iterative processes. Even more importantly, we’ll see that data frames are actually a very specific kind of list – one comprised of vectors of the same length – which is why they can store variables of different types.



## `for` loop

For this example, I’m going to start with the list defined below.

```{r}
list_norms = 
  list(
    a = rnorm(20, 3, 1),
    b = rnorm(20, 0, 5),
    c = rnorm(20, 10, .2),
    d = rnorm(20, -3, 1)
  )

is.list(list_norms)
```

```{r}
list_norms
```

I’d like to apply my simple `mean_and_sd` function from writing functions to each element of this list For completeness, that function is below.

```{r}
mean_and_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } 
  
  if (length(x) == 1) {
    stop("Cannot be computed for length 1 vectors")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)

  tibble(
    mean = mean_x, 
    sd = sd_x
  )
}
```

We can apply the `mean_and_sd` function to each element of list_norms using the lines below.

```{r}
mean_and_sd(list_norms[[1]])
mean_and_sd(list_norms[[2]])
mean_and_sd(list_norms[[3]])
mean_and_sd(list_norms[[4]])
```

Let's used a `for` loop.

Below, I define an output list with the same number of entries as my target dataframe; a sequence to iterate over; and a for loop body that applies the `mean_and_sd` function for each sequence element and saves the result. This will be much cleaner than using four almost-identical lines of code

```{r}
output = vector("list", length = 4)

for (i in 1:4) {
  output[[i]] = mean_and_sd(list_norms[[i]])
}
```

We already have our input list, `list_norms`. In the above code, we are creating the output list. Creating a vector that is a list, and the length equals to 4. The length just equal the length of input list. **`vector(mode = "logical/list etc", length = )`**


## maps

The **first argument** to `map()` is the list (or vector, or data frame) we want to iterate over, and the **second argument** is the function we want to apply to each element.

This following code will produce the same results as the above chuck, but `map` will track the name better, and you don't need to define your output vector / list. Since our input list has **a, b, c, d**, the `map` output will also name their results as **$a, $b, $c, $d**.

```{r}
output = map(list_norms, mean_and_sd)
```

It’s sometimes necessary to be more specific in giving arguments to `map`. In particular, using `.x = list_norms` for the input list and `~ mean_and_sd(.x)` to *specify the function applied to the input list* (using .x as a placeholder) will produce the same result.

```{r}
output = map(.x = list_norms, ~ mean_and_sd(.x))
```

### What if we want a different function? 
Functions can be passed as arguments to other functions. 

```{r}
output = map(list_norms, median)
```

## `map` variants

There are some useful variants to the basic map function if you know what kind of output you’re going to produce. 

The above is a list. Below we use `map_dbl` because *median outputs a single numeric value each time*. The result is a vector instead of a list. 
```{r}
output = map_dbl(list_norms, median)
```
Note: If we tried to use `map_int` or `map_lgl`, we’d get an error because the output of median isn’t a integer or a logical. 

Similarly, since we know `mean_and_sd` produces a data frame, we can use the output-specific `map_df` to change it to a datafram(df). Using the `.id` argument **keeps the names of the elements in the input list**.

```{r}
output = map_df(list_norms, mean_and_sd, .id = "input")
```

Lastly, the variant `map2` (and `map2_dbl`, etc) is helpful **when your function has two arguments**. In these cases, I find it best to be specific about arguments using something like the following:

```{r eval=FALSE}
output = map2(.x = input_1, .y = input_2, ~func(arg_1 = .x, arg_2 = .y))
```

## List columns and operation

```{r}
listcol_df = 
  tibble(
    name = c("a", "b", "c", "d"),
    samp = list_norms
  )
```

The `name` column is a character column. If you pull `name` column from the `listcol_df` data frame, the result is a character vector. Similarly, the `samp` column is a list column. You can also do some operation on it, such as `filter` or only examine the first list.

```{r}
listcol_df %>% pull(name)
listcol_df %>% pull(samp)

listcol_df %>% 
  filter(name == "a")

listcol_df$samp[[1]]
```


You can manipulate list columns, but usual operations for columns that might appear in mutate (like `mean` or `recode`) often *don’t apply to the entries in a list column*. Instead, recognizing list columns as list columns motivates alternative ways to work with them.

Let’s apply `mean_and_sd` to the first element of our list column.

```{r}
mean_and_sd(listcol_df$samp[[1]])
```

Keeping in mind that `listcol_df$samp` is a list, we can apply `mean_and_sd` function to each element using **`map`**.

```{r}
map(listcol_df$samp, mean_and_sd)
```

We’ve been using `mutate` to define a new variable in a data frame, especially one that is a function of an existing variable. We can also use `mutate` to add list columns in data frame. 

```{r}
listcol_df = 
  listcol_df %>% 
  mutate(summary = map(samp, mean_and_sd),
         medians = map_dbl(samp,median))

listcol_df
```




