---
title: "Simulation"
author: "Tianyou Wang"
date: "2022-11-25"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(rvest)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

set.seed(1)
```

Note: `set.seed(1)` setting will let R give you the same numbers for `rnorm` for every single time you knit your file.


## Simulation: Mean and SD for one n

In *writing functions* we wrote a short function to simulate data from a normal distribution, and return estimates of the mean and standard deviation.

```{r}
sim_mean_sd = function(n, mu = 2, sigma = 3) {
  
  sim_data = 
    tibble(
      x = rnorm(n, mean = mu, sd = sigma),
  )
  
  sim_data %>% 
    summarize(
      mu_hat = mean(x),
      sigma_hat = sd(x)
    )
}
```

```{r}
sim_mean_sd(30)
```

Let’s run `sim_mean_sd()` 100 times to see the effect of randomness in xi on estimates μ̂ ,σ̂ .

Start with a `for` loop.

```{r}
output = vector("list", 100)

for (i in 1:100) {
  output[[i]] = sim_mean_sd(30)
}

sim_results = bind_rows(output)
```

Let's use a loop function, `rerun`. This will give us the same thing. Note: `rerun(number of times, expressions to re-run)`

```{r}
sim_results = 
rerun(100, sim_mean_sd(n = 30)) %>% 
  bind_rows()
```

Let’s make some quick plots and compute some summaries for our simulation results.
```{r}
sim_results %>% 
  ggplot(aes(x = mu_hat)) +
  geom_density()

sim_results %>% 
  ggplot(aes(x = sigma_hat)) +
  geom_density()

sim_results %>% 
  summarize(
    avg_samp_mean = mean(mu_hat),
    sd_samp_mean = sd(mu_hat)
  )
```



## Simulation: Mean for several  n

```{r}
n_list = list(
  "n = 30" = 30,
  "n = 60" = 60,
  "n = 120" = 120,
  "n = 240" = 240
)

output = vector("list", length = 4)

output[[1]] = rerun(100, sim_mean_sd(n = n_list[[1]])) %>% 
  bind_rows()

output[[2]] = rerun(100, sim_mean_sd(n = n_list[[2]])) %>% 
  bind_rows()
```

To avoid using `output[[1]] = rerun(100, sim_mean_sd(n = n_list[[1]]))` multiple times, we gonna write a `for` loop.

```{r}
for (i in 1:4) {
  output[[i]] = rerun(100, sim_mean_sd(n = n_list[[i]])) %>% 
  bind_rows()
}
```

The above two chunks can also be down by this following code, use `expand_grid`.

```{r}
?expand_grid
```

```{r eval=FALSE}
sim_results_df = 
  expand_grid(
    sample_size = c(30, 60, 120, 240),
    iter = 1:1000
  ) %>% 
  mutate(
    estimate_df = map(sample_size, sim_mean_sd)
  ) %>% 
  unnest(estimate_df)
```

We want to track everything we have into a data frame.
```{r}
sim_results = 
tibble(
  sample_size = c(30, 60, 120, 240)
) %>% 
  mutate(
    output_lists = map(.x = sample_size, ~ rerun(1000, sim_mean_sd(.x))),
    estimate_df = map(output_lists, bind_rows)
  ) %>% 
  select(-output_lists) %>% 
  unnest(estimate_df)
```


Do some data frame things.

```{r}
sim_results %>% 
  mutate(
    sample_size = str_c("n = ", sample_size),
    sample_size = fct_inorder(sample_size)) %>% 
  ggplot(aes(x = sample_size, y = mu_hat, fill = sample_size)) + 
  geom_violin()
```

```{r}
sim_results %>% 
  group_by(sample_size) %>% 
  summarize(
    ave_samp_mean = mean(mu_hat),
    sd_samp_mean = sd(mu_hat)
  )
```



















