---
title: "Writing functions"
author: "Tianyou Wang"
date: "2022-11-18"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(rvest)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Do something simple

1. Creating a x vactor that's form a normal distribution. n = 30; mean = 5; std = 5.
2. Calculate the z-score = (x-mean)/std

```{r}
x_vec = rnorm(25, mean = 5, sd = 3)

(x_vec - mean(x_vec)) / sd(x_vec)
```

Now, we want to write a function to compute z-scores

```{r}
z_scores = function(x) {
  
  z = (x - mean(x)) / sd(x)
  
  return(z)
  
}

z_scores(x_vec)
```

* creating the `z_scorea` function and naming the input as `x`
* run the function `z_scorea` on our `x_vec`, which will give us the same answer as above


Let's try with a few samples and confirm that it works. `error=TRUE` allow the R_markdown to run with errors and show these errors. 
```{r error=TRUE}
z_scores(3)
z_scores("my name is jeff")
z_scores(iris)
z_scores(c(TRUE, TRUE, FALSE, TRUE))
z_scores(sample(c(TRUE, FALSE), 25, replace = TRUE))
```

* `z_scores(3)` is `NA` since the std for 3 is `NA`
* `z_scores("my name is jeff")` is not working, since it is not numeric
* `z_scores(iris)` is not working, since we cannot get the mean for a whole dataframe
* `z_scores(c(TRUE, TRUE, FALSE, TRUE))` is working because R see them as 0 or 1. **However**, it should not work. 

**So we need to add conditions in our function.**

```{r}
z_scores = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Z scores cannot be computed for length 1 vectors")
  }
  
  z = mean(x) / sd(x)
  
  z
}

z_scores(x_vec)
```

```{r error=TRUE}
z_scores(3)
z_scores("my name is jeff")
z_scores(mtcars)
z_scores(c(TRUE, TRUE, FALSE, TRUE))
z_scores(sample(c(TRUE, FALSE), 25, replace = TRUE))
```






