---
title: "Writing functions"
author: "Tianyou Wang"
date: "2022-11-18"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(rvest)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Do something simple

1. Creating a x vactor that's form a normal distribution. n = 30; mean = 5; std = 5.
2. Calculate the z-score = (x-mean)/std

```{r}
x_vec = rnorm(25, mean = 5, sd = 3)

(x_vec - mean(x_vec)) / sd(x_vec)
```

Now, we want to write a function to compute z-scores

```{r}
z_scores = function(x) {
  
  z = (x - mean(x)) / sd(x)
  
  return(z)
  
}

z_scores(x_vec)
```

* creating the `z_scorea` function and naming the input as `x`
* run the function `z_scorea` on our `x_vec`, which will give us the same answer as above


Let's try with a few samples and confirm that it works. `error=TRUE` allow the R_markdown to run with errors and show these errors. 
```{r error=TRUE}
z_scores(3)
z_scores("my name is jeff")
z_scores(iris)
z_scores(c(TRUE, TRUE, FALSE, TRUE))
z_scores(sample(c(TRUE, FALSE), 25, replace = TRUE))
```

* `z_scores(3)` is `NA` since the std for 3 is `NA`
* `z_scores("my name is jeff")` is not working, since it is not numeric
* `z_scores(iris)` is not working, since we cannot get the mean for a whole dataframe
* `z_scores(c(TRUE, TRUE, FALSE, TRUE))` is working because R see them as 0 or 1. **However**, it should not work. 

**So we need to add conditions in our function.**

```{r}
z_scores = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Z scores cannot be computed for length 1 vectors")
  }
  
  z = mean(x) / sd(x)
  
  z
}

z_scores(x_vec)
```

```{r error=TRUE}
z_scores(3)
z_scores("my name is jeff")
z_scores(mtcars)
z_scores(c(TRUE, TRUE, FALSE, TRUE))
z_scores(sample(c(TRUE, FALSE), 25, replace = TRUE))
```



## Multiple outputs

In some cases it might be better to return the mean and standard deviation instead of the Z scores. A first option is to **store each of the values in a named list**, and to return that list. 

```{r}
mean_and_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Cannot be computed for length 1 vectors")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)

  list(mean = mean_x, 
       sd = sd_x)
}
```

Check if the function work.

```{r}
x_vec = rnorm(100, mean = 3, sd =4)
mean_and_sd(x_vec)
```

Alternatively, we might **store values in a data frame**, using `tibble()`.

```{r}
mean_and_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Cannot be computed for length 1 vectors")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)

  tibble(
    mean = mean_x, 
    sd = sd_x
  )
}
```

```{r}
mean_and_sd(x_vec)
```

In general, either of these will be fine; which one you choose will depend on what kind of values you want to return, and what you plan to do with the function itself. If you want to return the original sample along with the computed values, a list might make sense; if you plan to run your function a lot and study the results, having a data frame will make it easier to use other tools.



## Multiple Inputs

I’d like to have a function that takes a given sample size along with a true mean and standard deviation, simulates data from a normal distribution, and returns the estimated mean and standard deviation. I’ll start from the code below.

```{r}
sim_data = tibble(
  x = rnorm(n = 30, mean = 2, sd = 3)
)

sim_data %>% 
  summarize(
    mu_hat = mean(x),
    sigma_hat = sd(x)
  )
```

You should examine this code – make sure it “makes sense”, take a look at the result of computing the mean and standard deviation, etc. Once you’re satisfied, it’s time to wrap things up in a function. 

* to be able to change the sample size and parameters, we change them into arguments
* the code that simulates data and computes the sample mean and SD go in the body
* the return statement should include the estimates. 


A function that does all this, using default values for the mean and standard deviation, is below.

```{r}
sim_mean_sd = function(n, mu = 2, sigma = 3) {
  
  sim_data = tibble(
    x = rnorm(n, mean = mu, sd = sigma),
  )
  
  sim_data %>% 
    summarize(
      mu_hat = mean(x),
      sigma_hat = sd(x)
    )
}
```

* the inputs are `n`, `mu`, and `sigma`

Check the function

```{r}
sim_mean_sd(100, 6, 3)
```


